How Diverse is the MoMA: While Modern, Not Diverse in Its Artists and Directors

### 2023-04-18 outputs/paper/paper.qmd
- Started models section in paper - Removed MoMA artists dataset from analysis as it is unused

# Model

```{r}
#| label: fig-model
#| fig-cap: Linear regression model of 
#| echo: false

numeric_momadirectors_data <- 
  cleaned_momadirectors_data |>
  mutate(Gender = case_when(
    Gender == "Female" ~ 1,
    Gender == "Male" ~ 2,
  ))

potential_gender_model <-
  lm(
    formula = Gender ~ DepartmentBeginYear,
    data = numeric_momadirectors_data
  )

summary(potential_gender_model)
```

The goal of our modelling strategy is twofold. Firstly,...

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
gender_model <-
  readRDS(file = here::here("outputs/models/gender_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false
modelsummary::modelsummary(
  list(
    "First model" = gender_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

## Weaknesses and next steps

>>>>

# Model
The goal of our modelling strategy is twofold. Firstly,...

@@

```{r}
#| label: fig-model1
#| fig-cap: Linear regression model of the effect of time on the percentage of female MoMA directors
#| echo: false
#| eval: true
#| warning: false
#| message: false

model_directors_percentage_female <-
  readRDS(file = here::here("outputs/models/model_directors_percentage_female.rds"))
```
```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory model of percentage of female MoMA directors based on year"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = model_directors_percentage_female
  ),
  fmt = 2
)
```

```{r}
#| label: fig-model2
#| fig-cap: Linear regression model of the effect of exhibit year on the percentage of female MoMA artists
#| echo: false
#| eval: true
#| warning: false
#| message: false

model_exhibits_percentage_female <-
  readRDS(file = here::here("outputs/models/model_exhibits_percentage_female.rds"))
```
```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory model of percentage of female MoMA artists based on exhibit year"
#| warning: false

modelsummary::modelsummary(
  list(
    "Second model" = model_exhibits_percentage_female
  ),
  fmt = 2
)
```

```{r}
#| label: fig-model3
#| fig-cap: Linear regression model of the effect of time and percentage of female MoMA directors on the percentage of female MoMA artists selected for exhibits
#| echo: false
#| eval: true
#| warning: false
#| message: false

model_exhibits_on_directors <-
  readRDS(file = here::here("outputs/models/model_exhibits_on_directors.rds"))
```
```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory model of percentage of female MoMA artists based on exhibit year and percentage of female MoMA directors "
#| warning: false

modelsummary::modelsummary(
  list(
    "Third model" = model_exhibits_on_directors
  ),
  fmt = 2
)
```

@@

## Weaknesses and next steps
- a LOT of NAs in the exhibit dataset, especially regarding artist gender, so results are skewed bc of that 
- binary understanding of gender that is exclusive
